### 2022-11-14 dissertation/chapters/08-results.tex
🚧 (results): WIP writing up findings

\noindent
All the required background information on all the elements relevant to the empirical process have been presented in Chapters~\ref{chap:anns}-\ref{chap:probability}. The proposed \acf{BHH} was presented in Chapter~\ref{chap:bhh} and the design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}. The methodology presented a number of experiments to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics. The methodology also defined a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.

Finally, this chapter provides the outcome of these empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for the discussions. The output of the statistical analysis that yielded the results presented in the chapter is provided in Appendix~\ref{app:statistical_analysis}. The remainder of the chapter is structured as follows.

\begin{itemize}
	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}. Illustrations are provided to show the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.

	\item \textbf{Section \ref{sec:results:bhh_vs_low_level_heuristics}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics as it relates to all datasets. Three variants of the \acs{BHH} are included in these results. These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.

	\item \textbf{Section \ref{sec:results:bhh_variant_hp}} provides the results for the experimental group that analyses the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:bhh_variant_population}} provides the results for the experimental group that analyses the effects of the \textit{population size} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:bhh_variant_credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:bhh_variant_reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:bhh_variant_replay}} provides the results for the experimental group that analyses the effects of the \textit{replay window size} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:bhh_variant_reanalysis}} provides the results for the experimental group that analyses the effects of the \textit{reanalysis interval} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:bhh_variant_burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:bhh_variant_normalise}} provides the results for the experimental group that analyses the effects of the \textit{normalisation} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:bhh_variant_discounted_rewards}} provides the results for the experimental group that analyses the effects of the \textit{discounted rewards} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:overfitting}} provides a brief discussion on overfitting as it is observed for some of the empirical tests.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% METRICS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
	\caption{The average training loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:train_loss}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
	\caption{The average test loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:test_loss}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
	\caption{The average training accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:train_accuracy}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
	\caption{The average test accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:test_accuracy}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS ALPHAS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
	\caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
	\caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
	\caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
	\caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:8}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS THETAS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{0}$ (\acs{SGD}), given concentration parameter $\alpha_{0}$, sampled from the probability distribution $P(\theta_{0} \vert \alpha_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:theta:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{6}$ (\acs{Adam}), given concentration parameter $\alpha_{6}$, sampled from the probability distribution $P(\theta_{6} \vert \alpha_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:theta:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{7}$ (\acs{PSO}), given concentration parameter $\alpha_{7}$, sampled from the probability distribution $P(\theta_{7} \vert \alpha_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:theta:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{8}$ (\acs{GA}), given concentration parameter $\alpha_{8}$, sampled from the probability distribution $P(\theta_{8} \vert \alpha_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:theta:8}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS P_H (Priors)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$, sampled from the prior selection probability distribution $P(h_{0} \vert \theta_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$, sampled from the prior selection probability distribution $P(h_{6} \vert \theta_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$, sampled from the prior selection probability distribution $P(h_{7} \vert \theta_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$, sampled from the prior selection probability distribution $P(h_{8} \vert \theta_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:8}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS P_HgEC (Posterior)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{0} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{6} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{7} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{8} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0:8}
\end{figure}

\section{BHH vs. Low-Level Heuristics}\label{sec:results:bhh_vs_low_level_heuristics}

% Table generated by Excel2LaTeX from sheet 'results - test - loss'
\begin{table}[htbp]
	\centering
	\caption{Empirical results showing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
	\label{tab:results:standalone:metrics:test_loss}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{rlccc|c|c|c|c|c|ccccc}
			epoch                                                                          & 30                 &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
			                                                                               &                    &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
			                                                                               &                    & \multicolumn{1}{l}{\textbf{heuristic}}                                         &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\

>>>>

The required background information on all the elements relevant to the empirical process have been presented in Chapters~\ref{chap:anns}-\ref{chap:probability}. The proposed \acf{BHH} was presented in Chapter~\ref{chap:bhh} and the design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}. The methodology presented a number of experimental groups to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics. The methodology also defined a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.

Finally, this chapter provides the outcome of these empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for the discussions. The output of the statistical analysis that yielded the results that is presented in the chapter is provided in Appendix~\ref{app:statistical_analysis}. The remainder of the chapter is structured as follows.

\begin{itemize}
	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}. Illustrations are provided to show the change in parameter values to illustrate the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.

	\item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics as it relates to all datasets. Three variants of the \acs{BHH} are included in these results. These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.

	\item \textbf{Section \ref{sec:results:heuristic_pool}} provides the results for the experimental group that analyses the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:population}} provides the results for the experimental group that analyses the effects of the \textit{population size} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:replay}} provides the results for the experimental group that analyses the effects of the \textit{replay window size} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:reanalysis}} provides the results for the experimental group that analyses the effects of the \textit{reanalysis interval} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:normalise}} provides the results for the experimental group that analyses the effects of the \textit{normalisation} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:discounted_rewards}} provides the results for the experimental group that analyses the effects of the \textit{discounted rewards} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:divergence}} provides a brief discussion on divergence as it is observed for some of the empirical tests.

@@

This section provides the empirical results of the case study on the behaviour of the \acs{BHH} as it is used to train a \acs{FFNN} on the iris dataset. As a reminder, the iris dataset contains 150 records, split into a training dataset containing 120 records, and a test dataset that contains 30 records. The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process. Some noisiness can be expected as mini-batch training is executed with batch sizes of 30. The results that are presented are averaged over 30 independent runs.

Furthermore, the case study focuses on three different variants of the \acs{BHH}. These include the baseline configuration as was provided in Chapter~\ref{chap:bhh}, as well as a configuration that includes a ``long memory'' by setting the replay window size to 250, and a configuration that makes use of the \textit{symmetric} credit assignment strategy. These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment is chosen to illustrate a case where there \acs{BHH} does not reward good performance and does not yield a bias towards \index{heuristic}heuristics that perform well. This section is structured as follows.

\begin{itemize}
	\item \textbf{Section \ref{sec:results:case_study:performance_metrics}} provides illustrations and discussions around the outcomes of the performance metrics as obtained by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:concentration_parameters}} provides illustrations and discussions around the changes in concentration parameter values as a result of the learning process implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probabilities of \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:prior_selec_prob}} provides illustrations and discussions around the changes in the \textit{prior \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:posterior_selec_prob}} provides illustrations and discussions around the changes in the \textit{posterior \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% METRICS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Performance metrics}\label{sec:results:case_study:performance_metrics}

Figures~\ref{fig:results:case_study:train_loss}-\ref{fig:results:case_study:test_accuracy} provide illustrations of the train and test, loss and accuracy plots over 30 epochs and is illustrated in log scale. The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}. The noisiness that results from mini-batch training can be observed in Figure~\ref{fig:results:case_study:test_loss}. Figures~\ref{fig:results:case_study:train_accuracy} and~\ref{fig:results:case_study:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%. Although the \acs{BHH} was able to succesfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration. However, it should be noted from epochs 5 and onwards presented in Figure~\ref{fig:results:case_study:test_accuracy} that all the configurations of the \acs{BHH} was able to ``undo'' selections that yielded worse test loss results in the previous epoch. The sporadic, oscillating nature of the results later in the training process is simply a result of momentum that is maintained between low-level \index{heuristic}heuristics. For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions. The \acs{BHH} does not incorporate a \textit{move acceptance} strategy, whereby a heuristic's outcome is rejected if it does not improve on previous results, yielding a possibly worse loss measurement. A move acceptance strategy can be utilised on a validation set as a mechanism to approve or reject heuristic progressions from one step to the other.

Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figures~\ref{fig:results:case_study:train_loss}-\ref{fig:results:case_study:test_accuracy} only provide the outcomes of performance metrics at the end of each epoch. Further investigation is required at a mini-batch step level.

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
	\caption{The average training loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:train_loss}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
	\caption{The average test loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:test_loss}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
	\caption{The average training accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:train_accuracy}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
	\caption{The average test accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:test_accuracy}
\end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PARAMS ALPHAS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Concentration Parameters}\label{sec:results:case_study:concentration_parameters}

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, from which prior \textit{probabilities of selection probabilities} are sampled. Figures~\ref{fig:results:case_study:alpha:0}-\ref{fig:results:case_study:alpha:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, 8 respectively. Index 0, 6, 7, 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively and only represent a subset of the concentration parameters in $\boldsymbol{\alpha}$ and the \index{heuristic pool}heuristic pool. Simular illustrations for the other indices in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
	\caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
	\caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
	\caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
	\caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alpha:8}
\end{figure}

The first logical observation to be made from Figures~\ref{fig:results:case_study:alpha:0}-\ref{fig:results:case_study:alpha:8} is the step-wise increasing nature of $\boldsymbol{\alpha}$ for the long memory configuration (denoted \textit{bhh\_replay\_250}), illustrated in green. Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics. The values in $\boldsymbol{\alpha}$ is never reset to its initial value of 1, and thus $\boldsymbol{\alpha}$ continues to increase throughout the training process. However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$. The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}. Heuristics that perform will will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly that other heuristics that do not perform well.

The next observation that can be made is for the baseline configuration (denoted \textit{bhh\_baseline}) in red, and the symmetric credit assignment strategy configuration (denoted \textit{bhh\_credit\_symmetric}) in blue. Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1 as regular intervals. This interval is represented by the \textit{reanalysis} window size. The reanalysis window size dictates the frequency at which Bayesian analysis is conducated on the performance log, mainted by the \acs{BHH}. Bayesian analysis is used to update $\boldsymbol{\alpha}$. As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change. Notice that $\boldsymbol{\alpha} \geq 1$ for multiple indices, even after reanalysis. This is because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1 at the corresponding index in $\boldsymbol{\alpha}$ through the Bayesian analysis process. In a case where all 5 entities in the entity pool are allocated the same heuristic, for all 10 steps in the reanalysis windown, $\boldsymbol{\alpha} = 50$.

Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning. The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurance} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$). \index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the probabilistic sampling nature of the \acs{BHH}. Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PARAMS THETAS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Probabilities of Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}

This section provides a detailed investigation into the \textit{probabilities of selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process. As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves. The probability distribution of \index{heuristic}heuristic selection probabilities is denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.

Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8} provide illustrations of the probabilities of the selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs. These illustrations are presented in log scale. Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at index 0, 6, 7, 8 represent the probabilities of selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and the \index{heuristic pool}heuristic pool. Once again, simular illustrations for the other indices in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
